\chapter*{Preface}
\setheader{Preface}
This document contains the work done for my thesis for the completion of the Master of Science in Computer Science (Data Science track). 
The work was conducted and completed at the Pattern Recognition Laboratory (PRLab) at Delft University of Technology.
This research stemmed from my interest in cryptocurrencies, for which I am grateful in many ways.
My passion for software engineering and finance, as well as my fascination with machine learning, which I developed during my studies at TU Delft, drove me into advances in automated cryptocurrency trading.
I gained an understanding of some of the many concepts present in order-driven financial markets.
Soon I realized that market orders were the limiting factor for my strategies to become profitable, and that appropriate placements of limit orders would solve this problem.
But how?
This thesis attempts to provide answers to this question.
The work mainly concerns the transposition of a financial problem into the reinforcement learning context and the explorations that were necessary thereafter.
My efforts included work that is well summarized in the following quote from Marcos Lopez de Prado:
\begin{quote}
    It takes almost as much effort to produce one true investment strategy as to produce a hundred, and the complexities are overwhelming: data curation and processing, HPC infrastructure, software development, feature analysis, execution simulators, backtesting, etc. \cite{de2018advances}
\end{quote}
\noindent
Many times during this project, I was reminded how important software engineering skills are, how much time a small mistake can cost, and how crucial it is to pay attention to details.
I was able to strengthen my skills and expand my knowledge in mathematics and machine learning.
\\
\\
I am grateful for this journey and would like to thank my supervisor Marco Loog for his guidance and advice during this research.
Our meetings and reviews he provided me were always a great help and urged me to take the extra step and think outside of the box.
Additionally, I would also like to thank Johan Pouwelse, as my co-supervisor, for his equally valuable advice and perspective from an applied point of view.
Our meetings were always inspiring and pointed towards the practical applications of my research, which made it without doubt an even more enjoyable project.
I would also like to thank Mateusz Garbacz, with whom I had many discussions during our "hacker-nights"; he helped in this project by providing me with his perspective and creativity.
I should also mention Satoshi Nakamoto, whoever that may be, who is not only the father of Bitcoin but has also created a new field of research.
Last but not least, I would like to thank my friends and family for their moral support.

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, July 10, 2018
\makeatother}
\end{flushright}

